---
title: "Exposure Consequences - Statistics and Figures"
output:
  pdf_document: default
  html_notebook: default
  html_document:
    df_print: paged
---

# Overview

Here I collect the 'right' statistics and figures for the exposure consequences project.

As I think of it right now, we will have these

Figures:

1. Setup & Task
2. Reach Aftereffects
3. Localization
4. Correlation 

Maybe not the 4th one.

There will also be a *Table* with tasks, and their order and number of trials in both the classic and exposure version of the task.

Tables:

1. Task order

## Source scripts

All the scripts doing the statistics and figures are in separate R files, but here we will only see / do the ones that we think should go to the manuscript.

First we load those other scripts:

```{r}
source('shared.R') # functions used everywhere
source('nocursor.R') # functions for no-cursor reach data
source('localization.R') # functions for localization data
source('relateLocalizationNoCursors.R') # functions that correlate the two kinds of data
```

## Topics

In the manuscript we'll first show that there are motor changes after exposure training (with the no-cursor data) and then compare that with the classic. Second is the localization: a) localization shifts after exposure b) the shifts are the same/different from those after classic c) the effects are different across the workspace d) this pattern is indistinguishable / different from that after classic. A third topic might be if localization shifts can predict no-cursor changes. Here we'll also follow this order:

1. Reach aftereffects
2. Localization
3. Correlations


# Reach Aftereffects

Here is a plot, probably Figure 2:

```{r fig.width=10, fig.height=4}
plotReachAftereffects()
```

Messages of the figure:

- Panel A: there are substantial and persisting reach aftereffects
- Panel B: that are somewhat lower than those in classic (but not that much? but only for some targets?)

These claims require analyses.

First, we show that no-cursor reaches change direction after exposure training:

```{r}
assessNoCursorChange()
```


