---
title: "Exposure Consequences - Statistics and Figures"
output:
  word_document: default
  pdf_document: default
  html_document:
    df_print: paged
  html_notebook: default
---

# Overview

Here I collect the 'right' statistics and figures for the exposure consequences project.

Here are the planned figures and tables:

Figures:

1. Setup & Task
2. Reach Aftereffects
3. Localization
4. Correlation 

(Maybe not the 4th one.)

Tables:

1. Task order

## Source scripts

All the scripts doing the statistics and figures are in separate R files, but here we will only see / do the ones that we think should go to the manuscript.

First we load those other scripts:

```{r}
source('shared.R') # functions used everywhere
source('nocursor.R') # functions for no-cursor reach data
source('localization.R') # functions for localization data
source('relateLocalizationNoCursors.R') # functions that correlate the two kinds of data
```

## Topics

In the manuscript we'll first show that there are motor changes after exposure training (with the no-cursor data) and then compare that with the classic. Second is the localization: a) localization shifts after exposure b) the shifts are the same/different from those after classic c) the effects are different across the workspace d) this pattern is indistinguishable / different from that after classic. A third topic might be if localization shifts can predict no-cursor changes. Here we'll also follow this order:

1. Reach aftereffects
2. Localization
3. Correlations


# Reach Aftereffects

Here is a plot, probably Figure 2:

```{r fig.width=10, fig.height=4}
plotReachAftereffects()
```

Messages of the figure:

- Panel A: there are substantial and persisting reach aftereffects
- Panel B: that are somewhat lower than those in classic (but not that much? but only for some targets?)

These claims require analyses.

First, we show that no-cursor reaches change direction after exposure training:

```{r include=TRUE}
exposureNoCursorChange()
```

So this shows that whether or not the feedback was rotated mattered for the reach deviations in the exposure training group, i.e.: there are reach aftereffects.

The second analysis is to show that the reach aftereffects aren't all that different for first and later iterations of the rotated no-cursor tasks. (The baseline is always all aligned iterations of the task.)

```{r}
exposureAftereffectsPersistent()
```

So there is no effect of iteration here, which means the reach aftereffects are the same for the first iteration and the average across the other four iterations. We now also have enough power to see an effect of target angle (the generalization curve is not flat), but more importantly the effect of iteration is also not dependent on target.

Finally, we want to see if there is a difference between teh reach aftereffects observed after exposure training and those after classic training.

```{r}
exposureClassicReachAftereffects()
```

I'd have expected there to be some difference between the two training types, perhaps only in interaction with target, but that's not the case apparently.



